---
title: "Visualize Data"
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Your Turn 0

Confer with your group.

What relationship do you expect to see between engine
size (displ) and mileage (hwy)?

```{r}
mpg
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
# add your code here
```

## Your Turn 2

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

## Your Turn 3

What do each of these do?
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```

## Your Turn 4

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(mpg) + geom_point(aes(class, hwy))
```

## Your Turn 5

In your group, predict what this code will do.
Then run it.

```{r}
ggplot(mpg) +
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))
```

## Your Turn 6

Create the plot on the slide: a white density 2d overlaid with colored points.
Consult the cheat sheet, and then your neighbor.

```{r}
# add your code here
```

## Your Turn 7

If I run this code, what will ggplot2 put on the y axis?
Try it and see.

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```

## Challenge 1

Can you alter this code to make the plot on a slide?

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```

## Challenge 2

Can you alter this code to make the plot on a slide?

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```

## Challenge 3

Can you alter this code to make the plot on a slide?

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```

## Your Turn 8

What do each of these adjustments do?
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
p <- ggplot(diamonds, aes(x = cut, fill = clarity))

p + geom_bar(position = "stack")
p + geom_bar(position = "dodge")
p + geom_bar(position = "identity")
p + geom_bar(position = "fill")
```

## Your Turn 9

Make the plot on the slide of the density of diamond prices grouped
and colored by cut.

```{r}
# add your code here
```

## Your Turn 10

Experiment with labels, themes, and scales to make a more clear
graph

```{r}
# add your code here
```

## Your Turn 11

Save your last plot and then locate it in your files panel.

```{r}
# add your code here
```

## Your Turn 12

Create an interactive graph. Can you add an extra information to on-hover info? Can you restrict it to just class?

```{r}
p <- ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))

library(plotly)
ggplotly(p)
```

***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```

You can find more complex template in the cheat sheet.